Are shade leaves lying in wait? How instantaneous responses of mesophyll conductance to light availability in shade leaves impacts canopy carbon gain

### 2015-07-23 manuscript/manuscript_wtc3.Rmd
added equations in methods
air vars script added with met data download script

\
Second, leaf ^13^CO~2~ during C~3~ photosynthesis ($\delta$^13^C) is the resultant discrimination from CO~2~ diffusion from the atmosphere to the site of carboxylation, consisting or a series of fractionation steps described in [@evans1986carbon]. In this experiment, a modified form of this equation presented in [@tazoe2011using] with ternary effect corrections by [@farquhar2012ternary] was used such that:

$$
\begin{aligned}
\Delta^13 = &\frac{1}{1-t}a'+\frac{1}{1-t}((1+t)b-a')\frac{C_i}{C_a}\\
            &\frac{1+t}{1-t}\left(b-a'-\frac{eR_d}{A+R_d}\right)\frac{A}{g_mC_a}-\\
            &\frac{1+t}{1-t}\left(\frac{eR_D}{(A+R_d)C_a}(C_i-\Gamma_*)\right)- \frac{1+t}{1-t}\left(f\frac{\Gamma_*}{C_a}\right)\\
\end{aligned}
$$

@@

>>>>

\
Second, leaf ^13^CO~2~ during C~3~ photosynthesis ($\delta$^13^C) is the resultant discrimination from CO~2~ diffusion from the atmosphere to the site of carboxylation, consisting or a series of fractionation steps described in [@evans1986carbon]. In this experiment, a modified form of this equation presented in [@evans2013temperature] with ternary effect corrections by [@farquhar2012ternary] was used such that:

from Evans & Von Caemmerer
$\Delta$~o~ = $\Delta$~i~ - $\Delta$~gm~ - $\Delta$~e~ - $\Delta$~f~
where $\Delta$~o~ is the observed discrimation and  $\Delta$~i~, $\Delta$~gm~ , $\Delta$~e~ and $\Delta$~f~ are the contritbutions of fractionataion if C~i~=C~c~, g~m~, respiration and photorespiration, respectively. The equations for each are as follows:

$$
\begin{aligned}
\Delta = &\frac{1}{1-t}a'+\frac{1}{1-t}((1+t)b-a')\frac{C_i}{C_a}\\
            &\frac{1+t}{1-t}\left(b-a'-\frac{eR_d}{A+R_d}\right)\frac{A}{g_mC_a}-\\
            &\frac{1+t}{1-t}\left(\frac{eR_D}{(A+R_d)C_a}(C_i-\Gamma_*)\right)- \frac{1+t}{1-t}\left(f\frac{\Gamma_*}{C_a}\right)\\
\end{aligned}
$$

$$
\begin{aligned}
\Delta_i = &\frac{1}{1-t}a'+\frac{1}{1-t}((1+t)b-a')\frac{C_i}{C_a}\\
\end{aligned}
$$

$$
\begin{aligned}
\Delta_gm = &\frac{1+t}{1-t}\left(b-a'-\frac{eR_d}{A+R_d}\right)\frac{A}{g_mC_a}-\\

\end{aligned}
$$

$$
\begin{aligned}
\Delta_e = &\frac{1+t}{1-t}\left(\frac{eR_D}{(A+R_d)C_a}(C_i-\Gamma_*)\right)
\end{aligned}
$$

$$
\begin{aligned}
\Delta = &\frac{1}{1-t}a'+\frac{1}{1-t}((1+t)b-a')\frac{C_i}{C_a}\\
            &\frac{1+t}{1-t}\left(b-a'-\frac{eR_d}{A+R_d}\right)\frac{A}{g_mC_a}-\\
            &\frac{1+t}{1-t}\left(\frac{eR_D}{(A+R_d)C_a}(C_i-\Gamma_*)\right)- \frac{1+t}{1-t}\left(f\frac{\Gamma_*}{C_a}\right)\\
\end{aligned}
$$

$$
\begin{aligned}
\Delta_f = & \frac{1+t}{1-t}\left(f\frac{\Gamma_*}{C_a}\right)\\
\end{aligned}
$$

@@

discrimination contributions and \delta vs ci/ca go here
